Erosion of somatic tissue identity with loss of the X-linked intellectual disability factor KDM5C

### 2024-07-09 submission/manuscript.Rmd
editing results/figs 4-5

- **note: do Direct vs indirect DEGs motif analysis**
- However, it is currently unclear if KDM5C binds to all germline DEGs and if its binding is maintained at any germline genes in neurons.

Previous work suggests KDM5C represses germline genes during early development, as re-expression of KDM5C in knockout neuronal cultures fails to suppress hippocampal germline DEGs and KDM5C is not bound to their promoters in neurons[@scandagliaLossKdm5cCauses2017]. There is some evidence KDM5C binds to select germline gene promoters in ESCs[@scandagliaLossKdm5cCauses2017], including two recent independent screens that found KDM5C binds to Dazl's promoter[@guptaGenomewideScreenReveals2023; @aladhamiSystematicIdentificationFactors2023]. As KDM5C's binding at germline gene promoters has not been systematically characterized, it is currently unclear what types of germline genes KDM5C regulates and if its binding is maintained at any germline genes in neurons.

@@

To further characterize the mechanism behind _Kdm5c_-KO germline gene misexpression, we analyzed KDM5C chromatin immunoprecipitation followed by DNA sequencing (ChIP-seq) datasets in EpiLCs[@samantaActivationXistEvolutionarily2022] and primary neuron cultures (PNCs) from the cortex and hippocampus[@iwaseMouseModelXlinked2016]. EpiLCs had a higher total number of KDM5C peaks than PNCs (EpiLCs: `r nrow(KDM5C_ChIP_EpiLC)`, PNCs: `r nrow(KDM5C_ChIP_PNC)`, MACS2 q < 0.1 and fold enrichment > 1) and KDM5C was primarily localized to gene promoters in both cell types (EpiLCs: `r nrow(KDM5C_ChIP_EpiLC_promo)`, PNCs: `r nrow(KDM5C_ChIP_PNC_promo)` +/- `r promorange`kb from TSS), although PNCs showed increased localization to non-promoter regions (Figure 4A).

The majority of promoters bound by KDM5C in PNCs were also bound in EpiLCs (513 shared promoters), however a large portion of gene promoters were only bound by KDM5C in EpiLCs (3677 EpiLC only promoters) (Figure 4B). We then performed gene ontology analysis to compare the functions of genes bound by KDM5C at the promoter in different cell types. While there were no significant ontologies for genes with KDM5C only bound in PNCs, gene ontologies for peaks shared between PNCs and EpiLCs were enriched for functions involving nucleic acid turnover, such as deoxyribonucleotide metabolic process (GO:0009262, p.adjust = `r signif(getGO("deoxyribonucleotide metabolic process", GO_KDM5C_ChIP, 'p.adjust', "Shared"), 3)`) (Figure 4C). Germline-specific ontologies were only enriched in peaks unique to EpiLCs, such as meiotic nuclear division (GO: 0007127 p.adjust = `r signif(getGO("meiosis I", GO_KDM5C_ChIP, 'p.adjust', "EpiLC only"), 3)`) and meiotic cell cycle process (GO:1903046, p.adjust = `r signif(getGO("meiotic cell cycle process", GO_KDM5C_ChIP, 'p.adjust', "EpiLC only"), 3)`) (Figure 3C). When comparing KDM5C binding at all germline gene promoters, KDM5C was only bound to a subset of germline gene promoters in EpiLCs and was not bound to any in PNCs (Figure 4D). Together, this suggests KDM5C is recruited to a subset of germline gene promoters in EpiLCs, including meiotic genes, but does not regulate germline genes in neurons.

To determine if the germline mRNAs expressed in the _Kdm5c_-KO brain and EpiLCs are direct targets of KDM5C, we then compared KDM5C binding at RNA-seq DEG promoters (Figure 4E). About one third of EpiLC specific and brain-specific (hippocampus, amygdala, or both) germline DEGs were bound by KDM5C in EpiLCs (EpiLC only: `r 18/50*100`%, Brain only: `r signif(7/21*100,3)`%). Some notable differences in KDM5C binding for EpiLC-specific DEGs included _Dazl_ and _Stra8_, two key drivers of germline identity discussed above. Although both mRNAs are expressed in _Kdm5c_-KO EpiLCs, KDM5C is only bound to _Dazl_'s promoter and not _Stra8_'s in EpiLCs (Figure 4F). In contrast to the unique DEGs, 3 out of the 4 genes dysregulated in both the brain and EpiLCs bound by KDM5C (Figure 4G). Again, we did not observe any KDM5C binding at germline gene promoters in PNCs, even for brain-specific DEGs (Figure 4H). Altogether, this suggests the majority of germline mRNAs expressed in _Kdm5c_-KO cells are dysregulated independent of direct KDM5C recruitment to their promoters during embryogenesis.

@@

Although KDM5C is generally thought to supress transcription through erasure of histone 3 lysine 4 di- and trimethylation (H3K4me2/3)[@iwaseXLinkedMentalRetardation2007], recent studies in ESCs have suggested KDM5C's repression _Dazl_ is independent of its catalytic activity[@guptaGenomewideScreenReveals2023]. Somatic repression of germline genes is typically established during the transition between naive and primed pluripotency, which modeled in vitro as ESCs to EpiLC differentiation. In ESCs, chromatin regulators place repressive histone modifications at germline gene promoters, including histone 2A 119 monoubiquitination (H2AK119ub1) and histone 3 lysine 9 trimethylation (H3K9me3)[@endohPCGF6PRC1SuppressesPremature2017; @liuPolycombGroupProtein2020; @mochizukiRepressionGermlineGenes2021]. Germline genes are then silenced long-term in EpiLCs by _de novo_ placement of DNA CpG methylation[@mochizukiRepressionGermlineGenes2021]. It has been proposed KDM5C may promote germline gene silencing via H3K4me3 removal since DNA methylation is lost at select germline gene promoters in the hippocampus[@scandagliaLossKdm5cCauses2017] and H3K4me3 can impair DNA methylation placement[@otaniStructuralBasisRecognition2009; @guoStructuralInsightAutoinhibition2015]. However, KDM5C was recently shown to repress _Dazl_ in ESCs indepedent of its catalytic activity[@guptaGenomewideScreenReveals2023]. Because KDM5C's role in germline gene repression has only been characterized in ESCs and in the mature brain, it is currently unclear to what extent KDM5C is involved during transition between ESCs and EpiLCs and if its catalytic activity is required for long-term silencing.

To elucidate KDM5C's role in germline gene silencing, we first characterized KDM5C's substrates, histone 3 lysine 4 di- and trimethylation (H3K4me2/3) in our previously published ChIP-seq datasets in wild type and _Kdm5c_-KO amygdala[@vallianatosMutuallySuppressiveRoles2020] and EpiLCs[@samantaActivationXistEvolutionarily2022]. In congruence with previous work in the _Kdm5c_-KO hippocampus[@scandagliaLossKdm5cCauses2017], we observed aberrant accumulation of H3K4me3 around the transcription start site (TSS) of germline genes in the _Kdm5c_-KO amygdala (Figure 5A). We additionally found a marked increase in H3K4me2 germline gene TSSs in _Kdm5c_-KO EpiLCs (Figure 5B). Incerase in H3K4me2 and H3K4me3 was highest in _Kdm5c_-KO cells that were highest genes that are bound by KDM5C at their promoter in EpiLCs (**note: do analysis to check if true**).

To assess KDM5C's embryonic role in germline gene silencing, we first characterized KDM5C's expression in ESCs and EpiLCs by harvesting RNA and protein at 0 hours (ESCs), 24 hours, and 48 hours (EpiLCs). While _Kdm5c_ mRNA steadily decreased from 0 to 48 hours of diferentiation, KDM5C protein initially increased from 0 to 24 hours but then decreased to near knockout levels by 48 hours (Figure 5C).

We then determined the role of KDM5C in the initial placement of DNA methylation at germline gene promoters by performing whole genome bislufite sequencing in wild-type and _Kdm5c_-KO ESCs and 96 hour extended EpiLCs (exEpiLCs) (**note: check**).
- While wild-type cells accumulate high levels of DNA methylation over the course of ESCs to exEpiLC differentiation, DNA methylation is markedly reduced in _Kdm5c_-KO

# Discussion
Random thoughts
- The demarcation of the germ vs soma is a key feature of multicellularity
- Anything known about tissue-biased gene expression in other H3K4me regulators?
- Our data suggests the germline developmental program is occuring ectopically as _Kdm5c_-KOs progresses through somatic tissue development
- tissue-biased gene expression:
	- However unlike the gonadal-biased DEGs, many liver and muscle-biased DEGs have a known involvement in brain function. For example, the liver-biased DEG is _Apolipoprotein C-I (Apoc1)_, is important for lipoprotein metabolism but has also been shown to influence learning and memory.
- Otx2 is expressed in EpiLCs and is known to repress PGC identity. 
	- It's properly expressed in _Kdm5c_-KO EpiLCs, further supporting they aren't just becoming PGCs https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6485399/

@@

\begin{figure}
  \centering 
  \includegraphics{../submission/compiled_figs/KDM5C_ChIPseq.pdf}
  \caption[KDM5C binds to a subset of germline gene promoters during early embryogenesis]{\textbf{KDM5C binds to a subset of germline gene promoters during early embryogenesis A.} ChIPseeker localization of KDM5C peaks at different genomic regions in EpiLCs (top) and hippocampal and cortex primary neuron cultures (PNCs, bottom). \textbf{B.} Overlap of genes with KDM5C bound to their promoters in EpiLCs (purple) and PNCs (blue). \textbf{C.} Gene ontology (GO) comparision of genes with KDM5C bound to their promoter. Genes were classified as either bound in EpiLCs only (EpiLC only), unique to PNCs (PNC only, no significant ontologies) or bound in both PNCs and EpiLCs (shared). \textbf{D.} Average KDM5C binding at all germline-enriched genes in EpiLCs (left) and PNCs (right). \textbf{E.} KDM5C binding at the promoters of RNA-seq germline DEGs. Genes were classified as either only dysregulated in EpiLCs (EpiLC only), genes dyresgulated in the hippocampus or amygdala but not EpiLCs (brain only), or genes dysregulated in both EpiLCs and the brain (common). (Legend continued on next page.)}
  \label{figurelabel}
\end{figure}
\addtocounter{figure}{-1}
\begin{figure} [t!]
  \caption[]{\textbf{KDM5C binds to a subset of germline gene promoters during early embryogenesis.} (Legend continued.) \textbf{F.} Example ChIP-seq bigwigs of DEGs unqiue to EpiLCs. Although both are expressed in EpiLCs, KDM5C is bound to the \textit{Dazl} promoter but not the \textit{Stra8} promoter in EpiLCs. \textbf{F.} Bigwigs of the upregulated imprinted gene \textit{Dlk1} that shows rescue in the double mutant brain. \textbf{G.} Example ChIP-seq bigwigs of DEGs common between brain and EpiLCs. KDM5C is bound to the \textit{D1Pas1} promoter but not the \textit{XXX} promoter in EpiLCs. \textbf{H.} Example ChIP-seq bigwigs of DEGs unique to the brain. KDM5C is bound to the \textit{XXX} promoter but not the \textit{Meig1} promoter}
\end{figure}

\newpage
\begin{figure}
  \centering
  \includegraphics{../submission/compiled_figs/KDM5C_Mechanism.pdf}
  \caption[KDM5C’s catalytic activity promotes long-term silencing of germline genes via DNA methylation]{\textbf{KDM5C’s catalytic activity promotes long-term silencing of germline genes via DNA methylation.} \textbf{A.} Left - Bigwigs of representative histone 3 lysine 4 trimethylation (H3K4me3) ChIP-seq peaks at two germline genes in the wild-type (WT) and \textit{Kdm5c}-KO (5CKO) adult amygdala. Right - Average H3K4me3 at the transcripiton start site (TSS) of all germline-enriched genes in wild-type (dark red) and \textit{Kdm5c}-KO amygdala. \textbf{B.} Left - Bigwigs of representative histone 3 lysine 4 dimethylation (H3K4me2) ChIP-seq peaks at representative germline genes in wild-type and \textit{Kdm5c}-KO EpiLCs. \textbf{C.} RNA and protein expression of KDM5C across ESC to EpiLC differentiation. Top left - diagram of differentiation protocol and collection time points. Bottom left - representative lanes of Western blot for KDM5C and DAXX. Middle - KDM5C protein expression normalized to DAXX. Quantified intensity using ImageJ (artificial units - au). Right - RT-qPCR of \textit{Kdm5c} RNA expression, calculated in comparision to TBP expression (2\textsuperscript{-deltaCT}) \textbf{D.} XXX {E.} XXX.}
  \label{figurelabel}
\end{figure}

>>>>

Previous work suggests KDM5C represses germline genes during early development, as re-expression of KDM5C in knockout neuronal cultures fails to suppress hippocampal germline DEGs and KDM5C is not bound to their promoters in neurons[@scandagliaLossKdm5cCauses2017]. There is some evidence KDM5C binds to select germline gene promoters in ESCs[@scandagliaLossKdm5cCauses2017], including _Dazl_[@guptaGenomewideScreenReveals2023; @aladhamiSystematicIdentificationFactors2023]. As KDM5C's binding at germline gene promoters has not been systematically characterized, it is currently unclear if KDM5C is enriched at germline gene promoters, what types of germline genes KDM5C regulates, and if its binding is maintained at any germline genes in neurons.

@@

To further characterize the mechanism behind _Kdm5c_-KO germline gene misexpression, we analyzed KDM5C chromatin immunoprecipitation followed by DNA sequencing (ChIP-seq) datasets in EpiLCs[@samantaActivationXistEvolutionarily2022] and primary neuron cultures (PNCs) from the cortex and hippocampus[@iwaseMouseModelXlinked2016]. EpiLCs had a higher total number of KDM5C peaks than PNCs (EpiLCs: `r nrow(KDM5C_ChIP_EpiLC)`, PNCs: `r nrow(KDM5C_ChIP_PNC)`, MACS2 q < 0.1 and fold enrichment > 1, removal of _Kdm5c_-KO false positive peaks) and KDM5C was primarily localized to gene promoters in both cell types (EpiLCs: `r nrow(KDM5C_ChIP_EpiLC_promo)`, PNCs: `r nrow(KDM5C_ChIP_PNC_promo)` +/- `r promorange`bp from the TSS), although PNCs showed increased localization to non-promoter regions (Figure 4A).

The majority of promoters bound by KDM5C in PNCs were also bound in EpiLCs (513 shared promoters), however a large portion of gene promoters were only bound by KDM5C in EpiLCs (3677 EpiLC only promoters) (Figure 4B). We then performed gene ontology analysis to compare the known functions of genes with KDM5C bound to their promoter in EpiLCs and PNCs. While there were no ontologies significantly enriched for genes only bound by KDM5C in PNCs, gene ontologies for genes shared between PNCs and EpiLCs were enriched for functions involving nucleic acid turnover, such as deoxyribonucleotide metabolic process (GO:0009262, p.adjust = `r signif(getGO("deoxyribonucleotide metabolic process", GO_KDM5C_ChIP, 'p.adjust', "Shared"), 3)`) (Figure 4C). Germline-specific ontologies were only enriched in promoters unique to EpiLCs, such as meiotic nuclear division (GO: 0007127 p.adjust = `r signif(getGO("meiosis I", GO_KDM5C_ChIP, 'p.adjust', "EpiLC only"), 3)`) and meiotic cell cycle process (GO:1903046, p.adjust = `r signif(getGO("meiotic cell cycle process", GO_KDM5C_ChIP, 'p.adjust', "EpiLC only"), 3)`) (Figure 3C). We then evaluated KDM5C binding around the transcription start site (TSS) of all germline-enriched genes. While KDM5C was bound to a subset of germline gene promoters in EpiLCs, it was not bound to any in PNCs (Figure 4D). Together, this suggests KDM5C is significantly enriched at a subset of germline gene promoters in EpiLCs, including meiotic genes, but does not regulate germline genes in neurons.

We then compared KDM5C binding at RNA-seq DEG promoters to determine if the germline mRNAs expressed in the _Kdm5c_-KO brain and EpiLCs are direct targets of KDM5C (Figure 4E). About one third of EpiLC-specific and brain-specific (hippocampus, amygdala, or both) germline DEGs were bound by KDM5C in EpiLCs (EpiLC only: `r 18/50*100`%, Brain only: `r signif(7/21*100,3)`%). Some notable differences in KDM5C binding for EpiLC-specific DEGs included _Dazl_ and _Stra8_, two key drivers of germline identity discussed above. Although both mRNAs are expressed in _Kdm5c_-KO EpiLCs, KDM5C is only bound to _Dazl_'s promoter and not _Stra8_'s in EpiLCs (Figure 4F). In contrast to the unique DEGs, 3 out of the 4 genes dysregulated in both the brain and EpiLCs are bound by KDM5C around the TSS (Figure 4G). Again, we did not observe any KDM5C binding at germline gene promoters in PNCs, even for brain-specific DEGs (Figure 4H). Altogether, this suggests the majority of germline mRNAs expressed in _Kdm5c_-KO cells are dysregulated independent of direct KDM5C recruitment to their promoters during embryogenesis.

**notes:**
- do Direct vs indirect DEGs motif analysis

@@

Although KDM5C is generally thought to supress transcription through erasure of histone 3 lysine 4 di- and trimethylation (H3K4me2/3)[@iwaseXLinkedMentalRetardation2007], recent studies in ESCs have suggested KDM5C's repression _Dazl_ is independent of its catalytic activity[@guptaGenomewideScreenReveals2023]. Somatic repression of germline genes is typically established during the transition between naive and primed pluripotency, which modeled _in vitro_ as ESCs to EpiLC differentiation. In ESCs, chromatin regulators place repressive histone modifications at germline gene promoters, including histone 2A 119 monoubiquitination (H2AK119ub1) and histone 3 lysine 9 trimethylation (H3K9me3)[@endohPCGF6PRC1SuppressesPremature2017; @liuPolycombGroupProtein2020; @mochizukiRepressionGermlineGenes2021]. Germline genes are then silenced long-term in EpiLCs by _de novo_ placement of DNA CpG methylation (DNAme)[@mochizukiRepressionGermlineGenes2021]. Although KDM5C's catalytic activity is not required to suppress _Dazl_ in ESCs, KDM5C may promote long-term germline gene silencing via H3K4me3 removal since H3K4me3 can impede DNAme placement[@otaniStructuralBasisRecognition2009; @guoStructuralInsightAutoinhibition2015] and DNAme is lost at select germline gene promoters in the hippocampus[@scandagliaLossKdm5cCauses2017]. Because KDM5C's role in germline gene repression has only been characterized in ESCs and in the mature brain, it is currently unclear to what extent KDM5C is involved during transition between ESCs and EpiLCs and if its catalytic activity is required for long-term silencing.

To elucidate KDM5C's role in germline gene silencing, we first characterized KDM5C's substrates, histone 3 lysine 4 di- and trimethylation (H3K4me2/3) in our previously published ChIP-seq datasets in wild type and _Kdm5c_-KO amygdala[@vallianatosMutuallySuppressiveRoles2020] and EpiLCs[@samantaActivationXistEvolutionarily2022]. In congruence with previous work in the _Kdm5c_-KO hippocampus[@scandagliaLossKdm5cCauses2017], we observed aberrant accumulation of H3K4me3 around the transcription start site (TSS) of germline genes in the _Kdm5c_-KO amygdala (Figure 5A). We additionally found a marked increase in H3K4me2 around the TSS of germline genes in _Kdm5c_-KO EpiLCs (Figure 5B).

We then evaluated KDM5C's embryonic role in germline gene silencing during ESC to EpiLC differentiation. We first characterized KDM5C's mRNA and protein expression at 0, 24, and 48 hours of differentiation (Figure 5C). While _Kdm5c_ mRNA steadily decreased from 0 to 48 hours of diferentiation (Figure 5D), KDM5C protein initially increased from 0 to 24 hours but then decreased to near knockout levels by 48 hours (Figure 5E). We then perfomed whole genome bislufite sequencing in wild-type and _Kdm5c_-KO ESCs and 96 hour extended EpiLCs (exEpiLCs) to determine KDM5C's role in the initial placement of DNA methylation at germline gene promoters. While wild-type cells accumulated high levels of DNA methylation at germline gene promoters over the course of ESCs to exEpiLC differentiation, DNA methylation was markedly reduced in _Kdm5c_-KO exEpiLCs (Figure 5F).

- Catalytic activity
- Altogether, this suggests KDM5C is dynamically regulated during ESC to EpiLC differentiation and promotes germline gene silencing via removal of H3K4me2/3 during early embryogenesis.

- **note:** should I test if incerase in H3K4me2 and H3K4me3 was highest in _Kdm5c_-KO cells at genes bound by KDM5C at their promoter in EpiLCs? Don't think it's that impactful

# Discussion

- The demarcation of the germ vs soma is a key feature of multicellularity
- Anything known about tissue-biased gene expression in other H3K4me regulators?
- Our data suggests the germline developmental program is occuring ectopically as _Kdm5c_-KOs progresses through somatic tissue development
- tissue-biased gene expression:
	- However unlike the gonadal-biased DEGs, many liver and muscle-biased DEGs have a known involvement in brain function. For example, the liver-biased DEG is _Apolipoprotein C-I (Apoc1)_, is important for lipoprotein metabolism but has also been shown to influence learning and memory.
- Otx2 is expressed in EpiLCs and is known to repress PGC identity. 
	- It's properly expressed in _Kdm5c_-KO EpiLCs, further supporting they aren't just becoming PGCs https://www.ncbi.nlm.nih.gov/pmc/articles/PMC6485399/

@@

\begin{figure}
  \centering 
  \includegraphics{../submission/compiled_figs/KDM5C_ChIPseq.pdf}
  \caption[KDM5C binds to a subset of germline gene promoters during early embryogenesis]{\textbf{KDM5C binds to a subset of germline gene promoters during early embryogenesis A.} ChIPseeker localization of KDM5C peaks at different genomic regions in EpiLCs (top) and hippocampal and cortex primary neuron cultures (PNCs, bottom). \textbf{B.} Overlap of genes with KDM5C bound to their promoters in EpiLCs (purple) and PNCs (blue). \textbf{C.} Gene ontology (GO) comparision of genes with KDM5C bound to their promoter in EpiLCs and PNCs. Genes were classified as either bound in EpiLCs only (EpiLC only), unique to PNCs (PNC only, no significant ontologies) or bound in both PNCs and EpiLCs (shared). \textbf{D.} Average KDM5C binding around the transcription start site (TSS) of all germline-enriched genes in EpiLCs (left) and PNCs (right). \textbf{E.} KDM5C binding at the promoters of RNA-seq germline DEGs. Genes were classified as either only dysregulated in EpiLCs (EpiLC only), genes dyresgulated in the hippocampus or amygdala but not EpiLCs (brain only), or genes dysregulated in both EpiLCs and the brain (common). (Legend continued on next page.)}
  \label{figurelabel}
\end{figure}
\addtocounter{figure}{-1}
\begin{figure} [t!]
  \caption[]{\textbf{KDM5C binds to a subset of germline gene promoters during early embryogenesis.} (Legend continued.) \textbf{F.} Example KDM5C ChIP-seq bigwigs of DEGs unqiue to EpiLCs. Although both are expressed in \textit{Kdm5c}-KO EpiLCs, KDM5C is only bound to the \textit{Dazl} promoter and not the \textit{Stra8} promoter in EpiLCs. \textbf{G.} Example KDM5C ChIP-seq bigwigs of RNA-seq DEGs common between the brain and EpiLCs. KDM5C is bound to the \textit{D1Pas1} promoter but not the \textit{XXX} promoter in EpiLCs. \textbf{H.} Example KDM5C ChIP-seq bigwigs of RNA-seq DEGs unique to the brain. KDM5C is bound to the \textit{XXX} promoter but not the \textit{Meig1} promoter}
\end{figure}

\newpage
\begin{figure}
  \centering
  \includegraphics{../submission/compiled_figs/KDM5C_Mechanism.pdf}
  \caption[KDM5C’s catalytic activity promotes long-term silencing of germline genes via DNA methylation]{\textbf{KDM5C’s catalytic activity promotes long-term silencing of germline genes via DNA methylation.} \textbf{A.} Left - Bigwigs of representative histone 3 lysine 4 trimethylation (H3K4me3) ChIP-seq peaks at two germline genes in the wild-type (WT) and \textit{Kdm5c}-KO (5CKO) adult amygdala. Right - Average H3K4me3 at the transcripiton start site (TSS) of all germline-enriched genes in wild-type (dark red) and \textit{Kdm5c}-KO (light red) amygdala. \textbf{B.} Left - Bigwigs of representative histone 3 lysine 4 dimethylation (H3K4me2) ChIP-seq peaks at representative germline genes in wild-type and \textit{Kdm5c}-KO EpiLCs. Right - Average H3K4me2 at the TSS of all germline-enriched genes in wild-type (dark purple) and \textit{Kdm5c}-KO (light purple) EpiLCs. \textbf{C.} Diagram of embryonic stem cell (ESC) to epiblast-like cell (EpiLC) differentiation protocol and collection time points for RNA and protein. \textbf{D.} Real time quantitative PCR (RT-qPCR) of \textit{Kdm5c} RNA expression, calculated in comparision to TBP expression (2\textsuperscript{-deltaCT}). * p < 0.05, ** p < 0.01, *** p < 0.001, Welch's t-test. \textbf{E.} KDM5C protein expression normalized to DAXX. Quantified intensity using ImageJ (artificial units - au). Right - representative lanes of Western blot for KDM5C and DAXX. * p < 0.05, ** p < 0.01, *** p < 0.001, Welch's t-test \textbf{F.} XXX {G.} XXX.}
  \label{figurelabel}
\end{figure}
